Missing Data: Current Practice in Football Research and Recommendations for

### 2020-11-07 paper/paper.Rmd
paper edits

---
title: 'Missing Data: Current Practice in Football Research and Recommendations for Improvement'
bibliography: references.bib
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  bookdown::pdf_document2:
    toc: no
  word_document:
    toc: yes
authors: David N Borg(1,2), Robert Nguyen(3), Nicholas J Tierney(4,5)
csl: sport-medicine.csl
---

>>>>

---
title: 'Missing Data: Current Practice in Football Research and Recommendations for
  Improvement'
bibliography: references.bib
csl: sport-medicine.csl
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  bookdown::pdf_document2:
    toc: no
  word_document:
    toc: yes
authors: David N Borg(1,2), Robert Nguyen(3), Nicholas J Tierney(4,5)
---
